Computing Entropies With Nested Sampling

### 2017-07-10 paper/ms.tex
1.5 paragraphs in Pareto section

\subsection{}

>>>>

The prior for $\alpha$ was chosen to be lognormal such that the prior median
of $\alpha$ is 1 and the prior standard deviation of $\ln \alpha$ is also 1.
Due to the heavy-tailed nature of the Pareto distribution, I ran the
algorithm in terms of $\ln \bar{y}$ and $\ln \bar{z}$. This affects the
differential entropies but not the mutual information (which is invariant 
under changes of parameterisation).

To compute the entropy of $\ln \bar{y}$, the distance function was just the
absolute value of the distance between the NS particles and the
reference particle in terms of $\ln \bar{y}$.
